A Survey of Near-Term Exoskeleton Technology\\ (Draft 3.0)

### 2015-09-29 technology.tex
more updates

We can consider the following combinaitons:
\begin{itemize}
\item
parallel combinations - fast but weak  actuator needs to hit joint limit and then be strong. (leads to chattering) or just lock in position to exert big force
\item
series combination - strong but slow actuator needs to clutch out of circuit to move fast
\end{itemize}

>>>>

We can consider the following combinaitons:
\begin{itemize}
\item
series combinations - fast but weak actuator needs to hit range limit and then be strong. (leads to chattering) or just lock in position to exert big force
\item
parallel combination - strong but slow actuator needs to clutch out of circuit to move fast
\end{itemize}
